%\documentclass[defaultstyle,11pt]{thesis}
\documentclass[defaultstyle,11pt]{thesis2side}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%  see documentation for information about  %%%%%%%%%%
%%%%%%%%%%%  the options (11pt, defaultstyle, etc.)   %%%%%%%%%%
%%%%%%%  http://www.colorado.edu/its/docs/latex/thesis/  %%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		\documentclass[typewriterstyle]{thesis}
% 		\documentclass[modernstyle]{thesis}
% 		\documentclass[modernstyle,11pt]{thesis}
%	 	\documentclass[modernstyle,12pt]{thesis}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%    load any packages which are needed    %%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{latexsym}		% to get LASY symbols
\usepackage{graphicx}		% to insert PostScript figures
\usepackage{subfigure}
\usepackage{rotating}		% for sideways tables/figures
\usepackage{color}
\usepackage{amssymb,amsmath}
\usepackage{url}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%       all the preamble material:       %%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Toward Continuously Variable Fidelity Wavelet-based Space/Time Adaptive DNS/CVS/LES Methodology}

\author{A}{Nejadmalayeri}

\otherdegrees{B.S., Amirkabir University of Technology (Tehran Polytechnic), 1999 \\
	      M.S., Wichita State University, 2007}

\degree{Doctor of Philosophy}       %  #1 {long descr.}
	{Ph.D., Mechanical Engineering}         %  #2 {short descr.}

\dept{Department of}                %  #1 {designation}
	{Mechanical Engineering}        %  #2 {name}

\advisor{Prof.}             %  #1 {title}
	{Oleg V. Vasilyev}      %  #2 {name}

\reader{Prof.~Gregory Beylkin}        %  2nd person to sign thesis
\readerThree{Prof.~Jem N. Corcoran}   %  3rd person to sign thesis
\readerFour{Prof.~Kurt Karl Maute}    %  4rd person to sign thesis
\readerFive{Prof.~Alireza Doostan}    %  5th person to sign thesis

\abstract{  \OnePageChapter	% one page only ??

The current work is an attempt to construct a wavelet-based variable fidelity approach
that provides a smooth transition amongst Wavelet-based Direct Numerical Simulation (WDNS), Coherent Vortex Simulations (CVS), and Stochastic Coherent Adaptive Large Eddy Simulations (SCALES)
based on the notion of spatially and temporarily varying wavelet thresholding which is proposed by this work.
%
The methodology provides an automatic transition from WDNS -- which provides a direct solution of wavelet filtered Navier-Stokes equations -- to coherent/incoherent flow decomposition in the CVS limit
to SCALES regime, where the  energy containing turbulent motions are resolved
%using wavelet multiresolution decomposition and self-adaptivity,
while the effect of less energetic motions is modeled.
%
The transition between WDNS, CVS, and SCALES regimes is achieved through two-way feedback between the modeled SGS dissipation
(or other dynamically important physical quantity) and the computational mesh.
The feedback is based on spatio-temporal variation of the wavelet threshold,
where the thresholding level is adjusted on the fly depending on
the deviation of local significant SGS dissipation from the user prescribed level.
%
This strategy overcome a major limitation for
all wavelet-based multi-resolution schemes: %for simulations of turbulence
the thresholding criterion is global and does not
fully utilize the spatial/temporal intermittency of the turbulent flow.
Hence, the aforementioned concept of physics-based spatially variable thresholding in the context of
wavelet-based numerical techniques for solving PDEs is introduced.
The procedure consists of tracking the wavelet thresholding-factor within a
Lagrangian frame by exploiting a Lagrangian Path-Line Diffusive Averaging
approach that uses linear averaging along characteristics.
%in order to adjust the thresholding-factor based on dynamically important flow characteristics,
%for instance, the magnitude of vorticity or strain rate.
%
This work is a preliminary study towards the construction of continuously
variable fidelity wavelet-based space/time/model-form adaptive  methodology.
}


%\dedication[Dedication]{	% NEVER use \OnePageChapter here.
%	To Neda.
%	}

%\acknowledgements{	\OnePageChapter	% *MUST* BE ONLY ONE PAGE!
%	Here's where you acknowledge folks who helped.
%This work was supported by the National Science Foundation (NSF) under grant No. CBET-0756046.
%}

\ToCisShort	% a 1-page Table of Contents ??

\LoFisShort	% a 1-page List of Figures ??
%	\emptyLoF	% no List of Figures at all ??

%\LoTisShort	% a 1-page List of Tables ??
	\emptyLoT	% no List of Tables at all ??


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%       BEGIN DOCUMENT...         %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%  footnote style; default=\arabic  (numbered 1,2,3...)
%%%%  others:  \roman, \Roman, \alph, \Alph, \fnsymbol
%	"\fnsymbol" uses asterisk, dagger, double-dagger, etc.
%	\renewcommand{\thefootnote}{\fnsymbol{footnote}}
%	\setcounter{footnote}{0}

\begin{document}

\input macros.tex               % file containing author's macro definitions
\input Chapter_01.tex           % file with Chapter 1 contents
\input Chapter_02.tex           % file with Chapter 2 contents
\input Chapter_03.tex           % file with Chapter 3 contents   Results adn Perpectives
\input Chapter_04.tex           % file with Chapter 4 contents   Perpectives and Proposal


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%  Bibliography %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{plain}	% or "siam", or "alpha", or "abbrv"
				% see other styles (.bst files) in
				% $TEXHOME/texmf/bibtex/bst

\nocite{*}		% list all refs in database, cited or not.

\bibliography{Comprehensive_bib}      % bib database file Comprehensive_bib.bib

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%  Appendices %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\appendix	% don't forget this line if you have appendices!

%\input appA.tex			% file with Appendix A contents
%\input appB.tex			% file with Appendix B contents

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%   THE END   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}
